### 2020-01-23 experiments.tex
nearly done

\begin{figure}
  \url{https://stackoverflow.com/questions/4297014/what-are-the-differences-between-pmd-and-findbugs}
  \url{https://www.sw-engineering-candies.com/blog-1/comparison-of-findbugs-pmd-and-checkstyle}
  \url{https://www.reddit.com/r/java/comments/3i7w6n/checkstyle_vs_pmd_vs_findbugs_for_dummies_why/}
\caption{Blog posts and forum threads discussing Java static analysis tools.}
\label{fig:blog}
\end{figure}

@@

\begin{figure}
  \url{https://stackoverflow.com/questions/1428872/pylint-pychecker-or-pyflakes}
  \url{https://www.reddit.com/r/Python/comments/ii3gm/experience_with_pylint_pychecker_pyflakes/}
  \url{https://www.slant.co/versus/12630/12631/~pylint_vs_pyflakes}
  \url{https://news.ycombinator.com/item?id=12748885}
  \url{https://doughellmann.com/blog/2008/03/01/static-code-analizers-for-python/}
\caption{Blog posts and forum threads discussing Python static analysis tools.}
\label{fig:blogpython}
\end{figure}

>>>>

\begin{figure}
  {\scriptsize
  \begin{itemize}
  \item \url{https://stackoverflow.com/questions/4297014/what-are-the-differences-between-pmd-and-findbugs}
  \item \url{https://www.sw-engineering-candies.com/blog-1/comparison-of-findbugs-pmd-and-checkstyle}
  \item \url{https://www.reddit.com/r/java/comments/3i7w6n/checkstyle_vs_pmd_vs_findbugs_for_dummies_why/}
  \end{itemize}
  }
\caption{Blog posts and forum threads discussing Java static analysis tools.}
\label{fig:blog}
\end{figure}

@@

\begin{figure}
  {\scriptsize
  \begin{itemize}
  \item \url{https://stackoverflow.com/questions/1428872/pylint-pychecker-or-pyflakes}
  \item \url{https://www.reddit.com/r/Python/comments/ii3gm/experience_with_pylint_pychecker_pyflakes/}
  \item \url{https://www.slant.co/versus/12630/12631/~pylint_vs_pyflakes}
  \item \url{https://news.ycombinator.com/item?id=12748885}
  \item \url{https://doughellmann.com/blog/2008/03/01/static-code-analizers-for-python/}
  \end{itemize}
  }
\caption{Blog posts and forum threads discussing Python static analysis tools.}
\label{fig:blogpython}
\end{figure}
